### 2021-09-29 README.Rmd
change out sydney for Fairfield in the README

```{r get-syd}
library(conmat)
sydney_age_pop <- abs_age_lga("Sydney (C)")
sydney_age_pop
```

@@

Then we take this model and extrapolate to the sydney data:

```{r sydney-synth-5}
set.seed(2021-09-24)
synthetic_settings_5y_sydney <- predict_setting_contacts(
  population = sydney_age_pop,
  contact_model = setting_models,
  age_breaks = c(seq(0, 85, by = 5), Inf)
  )

synthetic_settings_5y_sydney
```

```{r sydney-synth-5-plot}
# this code is erroring for the moment - something to do with rendering a large plot I think.
# plot_setting_matrices(
#   synthetic_settings_5y_sydney,
#   title = "Setting-specific synthetic contact matrices (Sydney 2020 projected)"
# )
```

```{r plot-matrix-differents}
set.seed(2021-09-24)
plot_matrix(synthetic_settings_5y_sydney$home)
plot_matrix(synthetic_settings_5y_sydney$work)
plot_matrix(synthetic_settings_5y_sydney$school)
plot_matrix(synthetic_settings_5y_sydney$other)
plot_matrix(synthetic_settings_5y_sydney$all)
```

>>>>

```{r get-syd}
library(conmat)
fairfield_age_pop <- abs_age_lga("Fairfield (C)")
fairfield_age_pop
```

@@

Then we take this model and extrapolate to the fairfield data:

```{r fairfield-synth-5}
set.seed(2021-09-24)
synthetic_settings_5y_fairfield <- predict_setting_contacts(
  population = fairfield_age_pop,
  contact_model = setting_models,
  age_breaks = c(seq(0, 85, by = 5), Inf)
  )
```

```{r fairfield-synth-5-plot}
# this code is erroring for the moment - something to do with rendering a large plot I think.
plot_setting_matrices(
  synthetic_settings_5y_fairfield,
  title = "Setting-specific synthetic contact matrices (fairfield 2020 projected)"
)
```

```{r plot-matrix-differents}
set.seed(2021-09-24)
plot_matrix(synthetic_settings_5y_fairfield$home)
plot_matrix(synthetic_settings_5y_fairfield$work)
plot_matrix(synthetic_settings_5y_fairfield$school)
plot_matrix(synthetic_settings_5y_fairfield$other)
plot_matrix(synthetic_settings_5y_fairfield$all)
```
